### 2013-01-20 edupar-13/outcomes.tex
outcomes.tex: This pass clarified (I hope), but produced no actual vertical shrinkage.

In this section we briefly describe selected
outcomes of the Spring 2012 offering of 15-410.
We begin by discussing the results of the
pre-Landslide educational experience and then
report on the results of applying Landslide to
kernels previously written by members of the course staff
and kernels written that semester by students.

@@

The SMP kernel-extension project
was a mixed success.
Of the twenty-four teams that attempted it,
one solo team was unable to submit a solution.
Nineteen of the remaining twenty-three groups
completed part of the project---at least enough to
boot multiple cores
\shortversion{}{(one, two, or eight depending on the simulator configuration)}
into their scheduler.
Four of those nineteen groups were able to run
almost all of our test suite of simple multi-threaded
applications.
Seven more groups were able to run roughly half of
the combinations of core counts versus test applications.
Finally, it was the sense of the grading team that
most groups would have been able to substantially complete
the project given a further week of development time.
We view this outcome as an indication that feasible adjustments
to the course design would bring this material within reach
of most students.

@@

We evaluated Landslide in two ways: first, by instrumenting two prior student kernels to measure the exploration time needed to find different races, and second, by meeting with current students of 15-410 in the Spring 2012 semester, before they submitted their kernel for grading, to see if they could find bugs on their own with Landslide.

In the first phase, we instrumented one kernel written by an author in a previous year, and also one kernel the same author manually graded as a teaching assistant.
We configured Landslide to search for five complicated well-known race conditions.
In addition to finding all five races, Landslide also found a sixth previously unknown race in said author's own kernel.
Using additional decision points only on calls to \x{mutex_lock}, Landslide found each of the six bugs in 11 to 57 seconds on a 2.6 GHz Xeon server, executing between 1 and 377 distinct interleavings for each.

>>>>

In this section we briefly describe selected
outcomes of the Spring 2012 offering of 15-410.
We begin by discussing the results of the
pre-Landslide educational experience and then
report on the results of applying Landslide to
both kernels previously written by members of the course staff
and kernels written that semester by students.

@@

The SMP kernel-extension project
was a mixed success.
Of the twenty-four teams that attempted it,
one (solo) team was unable to submit a solution.
Nineteen of the remaining twenty-three groups
completed part of the project---at least enough to
boot multiple cores
into their scheduler.
Four of those nineteen groups were able to pass
almost all of our test suite,
which consisted of simple multi-threaded applications
and machines with various core counts\shortversion
{.}
{(one, two, or eight depending on the simulator configuration).}
Seven more groups were able to pass roughly half of the test suite.
Finally, it was the sense of the grading team that
most groups would have been able to substantially complete
the project given a further week of development time.
We view this outcome as an indication that feasible adjustments
to the course design would bring this material within reach
of most students.

@@

We evaluated Landslide in two ways: first, by instrumenting two prior-semester student kernels to measure the exploration time needed to find different races, and second, by meeting with current-semester students, before they submitted their kernel for grading, to see if they could find bugs on their own with Landslide.

In the first phase, we instrumented one kernel written by a teaching assistant in a previous year, and also one student kernel later graded by that TA.
We configured Landslide to search for five complicated well-known race conditions.
In addition to finding all five races, Landslide also found a sixth previously unknown race in the TA's own kernel.
Using additional decision points only on calls to \x{mutex_lock}, Landslide found each of the six bugs in 11 to 57 seconds on a 2.6 GHz Xeon server, executing between 1 and 377 distinct interleavings per bug.
